### 2013-07-20 paper.tex
Very extended introduction.

\section{Preliminaries}
\label{sec:prelim}
% \subsection{Coxeter Rings, and the Bott-Samelson Bimodules}
Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in a real Euclidean space $V$, and let $\alpha_s$ and $\alpha_t$ be unit vectors normal to these planes.  We will assume that the angle formed by $\alpha_s$ and $\alpha_t$ is not a rational multiple of $\pi$, so that the order of $st$ in $W$ is infinite.  If $V$ has a positive definite symmetric bilinear form $(\mu, \lambda)$, then each $v \in V$ is reflected via the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a. \]  In particular, $s(\alpha_s) = -\alpha_s$ and $t(\alpha_t) = -\alpha_t$.  Furthermore, we see that there exist fixed constants $x$ and $y$ such that
\begin{align*}
	s(\alpha_t) &= \alpha_t + x \alpha_s \\
	t(\alpha_s) &= \alpha_s + y \alpha_t
\end{align*}
Now we define the \emph{Coxeter ring} by $R = \RR[\alpha_s, \alpha_t]$.  Then $W$ acts on $R$ by precisely the same algorithm as described above.

@@

\subsection{Diagrammatics of Maps}
\label{sec:prelim_map}
\newcommand{\DD}{\mathcal D}
Certain maps between Bott-Samleson bimodules can be described in terms of diagrams.  We take a detour and first describe the appearance of such diagrams; in the subsequent section we will explain their algebraic meaning.  A reader who is not interested in this context can simply accept on faith the relations specified in section \ref{sec:prelim_genrel}.

@@

\subsection{Algebraic Context}
The maps are conventionally read from bottom to top.  The labels on the upper and lower boundaries specify the domain and codomain of the map by simply transcribing the tensor products to take.  For example, a map with bottom $stt$ and top $s$ represents a map from $R \stimes R \ttimes R \ttimes R$ to $R \stimes R$.  An unlabelled domain corresponds to $R$.

@@

Subsequently, for any polynomial $f \in R$ we will abuse notation and refer to the map $x \mapsto fx$ by simply $f$.  In particular, one can easily verify that $\barbell{barbell_blue}$ represents $\alpha_s$.  Note that this is \emph{not} in general the same as $x \mapsto xf$ because $x$ may belong to some bimodule rather than to $R$.  Phrased diagrammatically, $\barbell{alpha_blue}\barbell{barbell_blue} \neq \barbell{barbell_blue}\barbell{alpha_blue} = \alpha_s$, for instance.

\subsection{Operations for Diagrammatics}
\label{sec:prelim_genrel}
From the algebraic context given above, one can derive the following relationships, which are here encoded completely graphically.  These rules are sufficient to compute the maps we are interested in.

@@

\subsection{Libedinsky's Light Leaves}
\label{sec:prelim_lightleave}
\begin{figure}[ht]
	\centering
	\begin{asy}
	size(10cm);
	real h = 0.7;
	pen s = blue, t = dashed + red + 0.6;
	int n = 14;
	draw(currentpicture, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
	draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
	draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
	draw(currentpicture, (4,0)--(4,h/2)..((4+8)/2.0,h*4)..(8,h/2)--(8,0), t);
	draw(currentpicture, (8,0)--(8,h/2)..((8+9)/2.0,h*1)..(9,h/2)--(9,0), t);
	draw(currentpicture, (11,0)--(11,h/2)..((11+13)/2.0,h*2)..(13,h/2)--(13,0), t);
	draw(currentpicture, (1,0)--(1,h), t);dot(currentpicture, (1,h), red);
	draw(currentpicture, (7,0)--(7,h), s);dot(currentpicture, (7,h), s);
	draw(currentpicture, (12,0)--(12,h), s);dot(currentpicture, (12,h), s);
	draw(currentpicture,(9,0)--(9,5*h), t);
	draw(currentpicture,(10,0)--(10,5*h), s);
	dot(currentpicture, (2, h/2), blue);
	dot(currentpicture, (8, h/2), red);
	dot(currentpicture, (9, h/2), red);
	label(currentpicture, "1", (0,-1.5h), dir(90));
	label(currentpicture, "s", (0,-0.8*h), dir(90));
	label(currentpicture, "0", (1,-1.5h), dir(90));
	label(currentpicture, "t", (1,-0.8*h), dir(90));
	label(currentpicture, "0", (2,-1.5h), dir(90));
	label(currentpicture, "s", (2,-0.8*h), dir(90));
	label(currentpicture, "1", (3,-1.5h), dir(90));
	label(currentpicture, "s", (3,-0.8*h), dir(90));
	label(currentpicture, "1", (4,-1.5h), dir(90));
	label(currentpicture, "t", (4,-0.8*h), dir(90));
	label(currentpicture, "1", (5,-1.5h), dir(90));
	label(currentpicture, "s", (5,-0.8*h), dir(90));
	label(currentpicture, "1", (6,-1.5h), dir(90));
	label(currentpicture, "s", (6,-0.8*h), dir(90));
	label(currentpicture, "0", (7,-1.5h), dir(90));
	label(currentpicture, "s", (7,-0.8*h), dir(90));
	label(currentpicture, "0", (8,-1.5h), dir(90));
	label(currentpicture, "t", (8,-0.8*h), dir(90));
	label(currentpicture, "0", (9,-1.5h), dir(90));
	label(currentpicture, "t", (9,-0.8*h), dir(90));
	label(currentpicture, "1", (10,-1.5h), dir(90));
	label(currentpicture, "s", (10,-0.8*h), dir(90));
	label(currentpicture, "1", (11,-1.5h), dir(90));
	label(currentpicture, "t", (11,-0.8*h), dir(90));
	label(currentpicture, "0", (12,-1.5h), dir(90));
	label(currentpicture, "s", (12,-0.8*h), dir(90));
	label(currentpicture, "1", (13,-1.5h), dir(90));
	label(currentpicture, "t", (13,-0.8*h), dir(90));
	\end{asy}
	\caption{An example of light leaves.}
	\label{fig:lightleaf_example}
\end{figure}

@@

\subsection{Problem Statement}
\label{sec:prelim_probstate}
Recall that maps are multiplied by simply placing them on top of each other.  The operations are then applied to simplify the product.

@@

In this question, we will consider only maps with the same top, and we will also work \emph{modulo lower terms}.  This means that any map which has a component that touches either the top or bottom boundary exactly once will be treated as zero.  In that case, using the operations described in section \ref{sec:prelim_genrel}, we can reduce every map to simply multiplying by a polynomial on the left.  The goal is to then compute these polynomials using some combinatorial formula.

\section{Definitions and Notations}
\subsection{Notations for Strings}
For each positive integer $n$, let us define for convenience the strings
\[ \SS_n \defeq \underbrace{s \dots s}_{\text{$n$ $s$'s}} \] 
and the ``alternating'' string
\[
	\AA_n \defeq
	\begin{cases}
		\underbrace{sts\dots s}_{\text{$n$ letters}} & \text{if } n \equiv 1 \pmod{2} \\
		\underbrace{sts\dots t}_{\text{$n$ letters}} & \text{if } n \equiv 0 \pmod{2} \\
	\end{cases}.
\]
By the way, let $\BB_n$ denote the set of binary strings of length $n$.

@@

\subsection{Definitions for Maps and Diagram}
Consider a string $\ul r$ of letters $s$ and $t$.  Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the appropriate map (or its associated diagram;
we will refer to maps and their associated diagrams interchangably) formed by a single application of the light leaves.  We will refer to such structures as \emph{half-maps} or \emph{half-diagrams} should such a need arise.  Additionally, let $\Top_{\ul r} \ul b$ denote the top of the half-diagram $\MM_{\ul r}(\ul b)$.

Then given two binary strings $\ul a$ and $\ul b$, we will let $\MM_{\ul r}(\ul a, \ul b)$ denote the product of $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ if $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, and $0$ otherwise.  (Recall that we are abusing notation in such products, and will simply refer to the map $g \mapsto fg$ as $f$ from this point on.)  Such structures will analogously be called \emph{full-maps} or \emph{full-diagrams} for clarity.  If $\ul r$ is clear from context, we will abbreviate $\MM_{\ul r}$ as simply $\MM$ and $\Top_{\ul r}$ as $\Top$.

@@

\subsection{Nomenclature for Certain Structures in Diagrams}
Let us make a few convenient definitions.

@@

\begin{definition*}
	A \emph{bubble} is a bounded face alongside with any components contained within it, which are its contents.  It may be connected to a fence, in which case we call it \emph{attached}.
\end{definition*}

@@

@@

Subsequently, we make the following definition.
\begin{definition*}
	For a binary string $\ul b$, define the \emph{partial-sum string} of $\ul b$, denoted $\ul b^\ast$, as follows:
	\[
		\ul b^\ast [i] = 
		\begin{cases}
			1 & \text{if } b[1] + b[2] + \dots + b[i] \equiv 1 \pmod{2} \\
			0 & \text{otherwise}
		\end{cases}.
	\]
\end{definition*}
This lets us state our main result for this section.
\begin{theorem}
	If $\ul a, \ul b \in \BB_n$ obey $\Top_{\SS_n} \ul a = \Top_{\SS_n} \ul b$, then
	\[
		\MM_{\SS_n} \left( \ul a, \ul b \right)
		=
		\begin{cases}
			0 & \text{if } \exists 1 \le i \le n-1: \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) - \ul a^\ast[n]} & \text{otherwise}
		\end{cases}.
	\]
\end{theorem}
\begin{figure}[ht]
	\centering
	\begin{asy}
		size(7cm);
		real h = 0.7;
		pen s = blue, t = red + dashed + 0.6;
		pen dot_s = blue, dot_t = red;
		int n = 8;
		draw(currentpicture, (0,0)--(0,h/2)..((0+1)/2.0,h*1)..(1,h/2)--(1,0), s);
		draw(currentpicture, (1,0)--(1,h/2)..((1+2)/2.0,h*1)..(2,h/2)--(2,0), s);
		draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
		draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
		draw(currentpicture, (4,0)--(4,h), s);
		dot(currentpicture, (4,h), dot_s);
		draw(currentpicture, (7,0)--(7,h), s);
		dot(currentpicture, (7,h), dot_s);
		dot(currentpicture, (1, h/2), dot_s);
		dot(currentpicture, (2, h/2), dot_s);
		label(currentpicture, "1", (0,-1.5h), dir(90));
		label(currentpicture, "s", (0,-0.8*h), dir(90));
		label(currentpicture, "0", (1,-1.5h), dir(90));
		label(currentpicture, "s", (1,-0.8*h), dir(90));
		label(currentpicture, "0", (2,-1.5h), dir(90));
		label(currentpicture, "s", (2,-0.8*h), dir(90));
		label(currentpicture, "1", (3,-1.5h), dir(90));
		label(currentpicture, "s", (3,-0.8*h), dir(90));
		label(currentpicture, "0", (4,-1.5h), dir(90));
		label(currentpicture, "s", (4,-0.8*h), dir(90));
		label(currentpicture, "1", (5,-1.5h), dir(90));
		label(currentpicture, "s", (5,-0.8*h), dir(90));
		label(currentpicture, "1", (6,-1.5h), dir(90));
		label(currentpicture, "s", (6,-0.8*h), dir(90));
		label(currentpicture, "0", (7,-1.5h), dir(90));
		label(currentpicture, "s", (7,-0.8*h), dir(90));
	\end{asy}
	\caption{It looks hard until you actually draw it.  Then you LOL.}
\end{figure}
\begin{proof}
	We will only consider the case where $\Top \ul a = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.

@@

\section{The Caterpillar Theorem}
\label{sec:caterpillar}
We now turn our attention to the case of $\ul r = \AA_n$.

>>>>

\section{Preliminaries and Definitions}
\subsection{An Extended Introduction}
\label{sec:prelim}
% \subsection{Coxeter Rings, and the Bott-Samelson Bimodules}
Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in a real Euclidean space $V$, and let $\alpha_s$ and $\alpha_t$ be unit vectors normal to these planes.  We will assume that the angle formed by $\alpha_s$ and $\alpha_t$ is not a rational multiple of $\pi$, so that the order of $st$ in $W$ is infinite.  If $V$ has a positive definite symmetric bilinear form $(\mu, \lambda)$, then each $v \in V$ is reflected via the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a. \]  In particular, $s(\alpha_s) = -\alpha_s$ and $t(\alpha_t) = -\alpha_t$.  Furthermore, we see that there exist fixed constants $x$ and $y$ such that
\begin{align*}
	s(\alpha_t) &= \alpha_t + x \alpha_s \\
	t(\alpha_s) &= \alpha_s + y \alpha_t
\end{align*}
Now we define the \emph{Coxeter ring} by $R = \RR[\alpha_s, \alpha_t]$.  Then $W$ acts on $R$ by precisely the same algorithm as described above.

@@

\subsubsection{Diagrammatics of Maps}
\label{sec:prelim_map}
\newcommand{\DD}{\mathcal D}
Certain maps between Bott-Samleson bimodules can be described in terms of diagrams.  We take a detour and first describe the appearance of such diagrams; in the subsequent section we will explain their algebraic meaning.  A reader who is not interested in this context can simply accept on faith the relations specified in section \ref{sec:prelim_genrel}.

@@

\subsubsection{Algebraic Context}
The maps are conventionally read from bottom to top.  The labels on the upper and lower boundaries specify the domain and codomain of the map by simply transcribing the tensor products to take.  For example, a map with bottom $stt$ and top $s$ represents a map from $R \stimes R \ttimes R \ttimes R$ to $R \stimes R$.  An unlabelled domain corresponds to $R$.

@@

% Subsequently, for any polynomial $f \in R$ we will abuse notation and refer to the map $x \mapsto fx$ by simply $f$.  In particular, one can easily verify that $\barbell{barbell_blue}$ represents $\alpha_s$.  Note that this is \emph{not} in general the same as $x \mapsto xf$ because $x$ may belong to some bimodule rather than to $R$.  Phrased diagrammatically, $\barbell{alpha_blue}\barbell{barbell_blue} \neq \barbell{barbell_blue}\barbell{alpha_blue} = \alpha_s$, for instance.

\subsubsection{Operations for Diagrammatics}
\label{sec:prelim_genrel}
From the algebraic context given above, one can derive the following relationships, which are here encoded completely graphically.  These rules are sufficient to compute the maps we are interested in.

@@

\subsubsection{Libedinsky's Light Leaves}
\label{sec:prelim_lightleave}
\begin{figure}[ht]
	\centering
	\begin{asy}
	size(10cm);
	real h = 0.7;
	pen s = blue, t = dashed + red + 0.6;
	int n = 14;
	draw(currentpicture, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
	draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
	draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
	draw(currentpicture, (4,0)--(4,h/2)..((4+8)/2.0,h*4)..(8,h/2)--(8,0), t);
	draw(currentpicture, (8,0)--(8,h/2)..((8+9)/2.0,h*1)..(9,h/2)--(9,0), t);
	draw(currentpicture, (11,0)--(11,h/2)..((11+13)/2.0,h*2)..(13,h/2)--(13,0), t);
	draw(currentpicture, (1,0)--(1,h), t);dot(currentpicture, (1,h), red);
	draw(currentpicture, (7,0)--(7,h), s);dot(currentpicture, (7,h), s);
	draw(currentpicture, (12,0)--(12,h), s);dot(currentpicture, (12,h), s);
	draw(currentpicture,(9,0)--(9,5*h), t);
	draw(currentpicture,(10,0)--(10,5*h), s);
	dot(currentpicture, (2, h/2), blue);
	dot(currentpicture, (8, h/2), red);
	dot(currentpicture, (9, h/2), red);
	label(currentpicture, "1", (0,-1.5h), dir(90));
	label(currentpicture, "s", (0,-0.8*h), dir(90));
	label(currentpicture, "0", (1,-1.5h), dir(90));
	label(currentpicture, "t", (1,-0.8*h), dir(90));
	label(currentpicture, "0", (2,-1.5h), dir(90));
	label(currentpicture, "s", (2,-0.8*h), dir(90));
	label(currentpicture, "1", (3,-1.5h), dir(90));
	label(currentpicture, "s", (3,-0.8*h), dir(90));
	label(currentpicture, "1", (4,-1.5h), dir(90));
	label(currentpicture, "t", (4,-0.8*h), dir(90));
	label(currentpicture, "1", (5,-1.5h), dir(90));
	label(currentpicture, "s", (5,-0.8*h), dir(90));
	label(currentpicture, "1", (6,-1.5h), dir(90));
	label(currentpicture, "s", (6,-0.8*h), dir(90));
	label(currentpicture, "0", (7,-1.5h), dir(90));
	label(currentpicture, "s", (7,-0.8*h), dir(90));
	label(currentpicture, "0", (8,-1.5h), dir(90));
	label(currentpicture, "t", (8,-0.8*h), dir(90));
	label(currentpicture, "0", (9,-1.5h), dir(90));
	label(currentpicture, "t", (9,-0.8*h), dir(90));
	label(currentpicture, "1", (10,-1.5h), dir(90));
	label(currentpicture, "s", (10,-0.8*h), dir(90));
	label(currentpicture, "1", (11,-1.5h), dir(90));
	label(currentpicture, "t", (11,-0.8*h), dir(90));
	label(currentpicture, "0", (12,-1.5h), dir(90));
	label(currentpicture, "s", (12,-0.8*h), dir(90));
	label(currentpicture, "1", (13,-1.5h), dir(90));
	label(currentpicture, "t", (13,-0.8*h), dir(90));
	\end{asy}
	\caption{An example of light leaves.}
	\label{fig:lightleaf_example}
\end{figure}

@@

\subsubsection{Problem Statement}
\label{sec:prelim_probstate}
Recall that maps are multiplied by simply placing them on top of each other.  The operations are then applied to simplify the product.

@@

Further details on the evaluation of these maps are detailed in section \ref{sec:explain_poly_eval}, but before that we need to introduce certain definitions for clarity.

% In this question, we will consider only maps with the same top, and we will also work \emph{modulo lower terms}.  This means that any map which has a component that touches either the top or bottom boundary exactly once will be treated as zero.  In that case, using the operations described in section \ref{sec:prelim_genrel}, we can reduce every map to simply multiplying by a polynomial on the left.  The goal is to then compute these polynomials using some combinatorial formula.

\subsection{Definitions and Notations}
\subsubsection{Notations for Strings}
For each positive integer $n$, let us define for convenience the strings
\[ \SS_n \defeq \underbrace{s \dots s}_{\text{$n$ $s$'s}} \] 
and the ``alternating'' string
\[
	\AA_n \defeq
	\begin{cases}
		\underbrace{sts\dots s}_{\text{$n$ letters}} & \text{if } n \equiv 1 \pmod{2} \\
		\underbrace{sts\dots t}_{\text{$n$ letters}} & \text{if } n \equiv 0 \pmod{2} \\
	\end{cases}.
\]
Let $\BB_n$ denote the set of binary strings of length $n$.

@@

\subsubsection{Definitions for Maps and Diagram}
Consider a string $\ul r$ of letters $s$ and $t$.  Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the appropriate map (or its associated diagram;
we will refer to maps and their associated diagrams interchangably) formed by a single application of the light leaves.  We will refer to such structures as \emph{half-maps} or \emph{half-diagrams} should such a need arise.  Additionally, let $\Top_{\ul r} \ul b$ denote the top of the half-diagram $\MM_{\ul r}(\ul b)$.

Then given two binary strings $\ul a$ and $\ul b$, we will let $\MM_{\ul r}(\ul a, \ul b)$ denote the product of $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ if $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, and $0$ otherwise.  % (Recall that we are abusing notation in such products, and will simply refer to the map $g \mapsto fg$ as $f$ from this point on.)  
Such structures will analogously be called \emph{full-maps} or \emph{full-diagrams} for clarity.  If $\ul r$ is clear from context, we will abbreviate $\MM_{\ul r}$ as simply $\MM$ and $\Top_{\ul r}$ as $\Top$.

@@

% We will now abuse notation further and refer even to components by polynomials, when the map is left alone.  For example, $\barbell{alpha_blue}\barbell{barbell_blue}\barbell{barbell_blue}\barbell{barbell_red}$ might be referred interchangeably with $\barbell{alpha_blue} \alpha_s^2 \alpha_t$.  Note that, even though we may write $\barbell{alpha_blue} = 1$, we still have $\barbell{alpha_blue} \alpha_s^2\alpha_t \neq \alpha_s^2\alpha_t$, because we strictly require left multiplication as the accepted convention.

\subsubsection{Nomenclature for Certain Structures in Diagrams}
Let us make a few convenient definitions.

@@

\begin{definition*}
	A \emph{bubble} is a bounded face alongside with any components contained within it, which are its \emph{contents}.  
\end{definition*}

@@

\subsection{Representations of Maps as Polynomials}
% TODO actually do this

@@

Subsequently, we make the following definition.
\begin{definition*}
	For a binary string $\ul b$, define the \emph{partial-sum string} of $\ul b$, denoted $\ul b^\ast$, as follows:
	\[
		\ul b^\ast [i] = 
		\begin{cases}
			1 & \text{if } b[1] + b[2] + \dots + b[i] \equiv 1 \pmod{2} \\
			0 & \text{otherwise}
		\end{cases}.
	\]
\end{definition*}
This lets us state our main result for this section.
\begin{theorem}
	If $\ul a, \ul b \in \BB_n$ obey $\Top_{\SS_n} \ul a = \Top_{\SS_n} \ul b$, then
	\[
		\MM_{\SS_n} \left( \ul a, \ul b \right)
		=
		\begin{cases}
			0 & \text{if } \exists 1 \le i \le n-1: \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) - \ul a^\ast[n]} & \text{otherwise}
		\end{cases}.
	\]
\end{theorem}
\begin{figure}[ht]
	\centering
	\begin{asy}
		size(7cm);
		real h = 0.7;
		pen s = blue, t = red + dashed + 0.6;
		pen dot_s = blue, dot_t = red;
		int n = 8;
		draw(currentpicture, (0,0)--(0,h/2)..((0+1)/2.0,h*1)..(1,h/2)--(1,0), s);
		draw(currentpicture, (1,0)--(1,h/2)..((1+2)/2.0,h*1)..(2,h/2)--(2,0), s);
		draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
		draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
		draw(currentpicture, (4,0)--(4,h), s);
		dot(currentpicture, (4,h), dot_s);
		draw(currentpicture, (7,0)--(7,h), s);
		dot(currentpicture, (7,h), dot_s);
		dot(currentpicture, (1, h/2), dot_s);
		dot(currentpicture, (2, h/2), dot_s);
		label(currentpicture, "1", (0,-1.5h), dir(90));
		label(currentpicture, "s", (0,-0.8*h), dir(90));
		label(currentpicture, "0", (1,-1.5h), dir(90));
		label(currentpicture, "s", (1,-0.8*h), dir(90));
		label(currentpicture, "0", (2,-1.5h), dir(90));
		label(currentpicture, "s", (2,-0.8*h), dir(90));
		label(currentpicture, "1", (3,-1.5h), dir(90));
		label(currentpicture, "s", (3,-0.8*h), dir(90));
		label(currentpicture, "0", (4,-1.5h), dir(90));
		label(currentpicture, "s", (4,-0.8*h), dir(90));
		label(currentpicture, "1", (5,-1.5h), dir(90));
		label(currentpicture, "s", (5,-0.8*h), dir(90));
		label(currentpicture, "1", (6,-1.5h), dir(90));
		label(currentpicture, "s", (6,-0.8*h), dir(90));
		label(currentpicture, "0", (7,-1.5h), dir(90));
		label(currentpicture, "s", (7,-0.8*h), dir(90));
	\end{asy}
	\caption{A half-map with base $\SS_8$.}
\end{figure}
\begin{proof}
	We will only consider the case where $\Top \ul a = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.

@@

\section{Constraints on the Diagrammatics in the Alternating Case}
\label{sec:caterpillar}
We now turn our attention to the case of $\ul r = \AA_n$.

In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
\begin{lemma}[Bubble Lemma]
	Consider a bubble in a full-diagram with base $\AA_n$.  The contents of the bubble are either a barbell or a caterpillar.
\end{lemma}
\begin{corollary}[Caterpillar Corollary]
	A caterpillar in a full-diagram with base $\AA_n$ evaluates as 
\end{corollary}<++>
